\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model
\red{Blablabla ... improve text ...} ... {\it The mesh adaptive algorithm embedded in the Fluidity/ICFERST model utilises a metric tensor field dependent on solution interpolation error-estimates \red{(talk about a posteriori errors and a short description of the mesh adaptivity algorithm)}\blue{(ref mesh adaptivity paper of 1995)} which locally control size and shape of elements in the metric. Mesh optimisation, based on XXX simulated annealing, is able to generate unstructured finer mesh grid in regions where flow properties change faster and coarser mesh grid in regions  where properties does not change so quickly.  }

>>>>

The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
